### 2014-05-08 intro.tex
Revise section heading
Add some results to sprout section of intro

\section{The benefits of showing our work as designers}

@@

Over the last three years, my colleagues and I have built a series of
systems to explore this approach:

@@

Mosh is primarily a remote terminal application and is not further
discussed in this dissertation, but its design ideas---maintain an
explicit model at runtime, and pursue a stated objective on behalf
of the user---formed the basis of our subsequent work on transport
protocol design.

\textbf{Sprout} (Chapter~\ref{chap:sprout}) is a transport protocol
designed to carry high-throughput interactive traffic, such as a
videoconference, over a cellular network. Sprout includes an explicit
model of the dynamics of cellular networks and makes predictions about
future network performance by inferring, with uncertainty, the current
state of the network and evolving the model forward. Its control
strategy---how much data to send at a given moment---is a function of
those predictions and of an explicit objective: maximize throughput,
but bound in-network delays to be at most 100~ms with high
probability. On commercial cellular networks, Sprout gives 2-to-4
times the throughput and 7-to-9 times less delay than Skype, Apple
Facetime, and Google Hangouts.

\textbf{Remy} (Chapter~\ref{chap:remy}) expands Sprout to the
classical problem of \emph{multi-agent} congestion control, where many
applications may contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of assumptions
about the uncertain network and workload, and an objective to pursue
on behalf of the application. Remy's computer-generated algorithms can
achieve higher performance and greater fairness than some
sophisticated human-designed schemes, including ones that put
intelligence inside the network.

>>>>

%\section{Showing our work in protocol design}

@@

\section{Summary of results}

Over the last three years, my colleagues and I have built a series of
systems to explore this approach.

\subsection{Mosh (2011)}

@@

By having an explicit model of the user interface at both sides of the
connection, the Mosh client is able to predict the application's
behavior in response to user keystrokes and (if confident in its
predictions) can speculatively display the result---generally an
echoed keystroke or cursor motion---before it has been confirmed by
the server. In practice, in a trace-based evaluation using 40 hours of
real-world usage, Mosh was able to show immediately the results of
\textbf{70\%} of user keystrokes.

Mosh is primarily a remote terminal application and is not further
discussed in this dissertation, but its design ideas---maintain an
explicit model at runtime, and pursue a stated objective on behalf of
the user---formed the basis of my subsequent work on
transport-protocol design.

\subsection{Sprout (2012)}

\textbf{Sprout} (Chapter~\ref{chap:sprout}) is a transport protocol
designed to carry high-throughput interactive traffic, such as a
videoconference, over a cellular network. Sprout includes an explicit
model of the dynamics of cellular networks and makes predictions about
future performance by inferring, with uncertainty, the current state
of the network and evolving the model forward. Its control
strategy---how much data to send at a given moment---is a function of
those predictions and of an explicit objective: maximize throughput,
but bound in-network delays to be at most 100~ms with high
probability.

In a trace-driven experimental evaluation (details in
\S\ref{sprout:eval}), Sprout gave 2-to-4 times the throughput and
7-to-9 times less delay than Skype, Apple Facetime, and Google
Hangouts:

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
Sprout vs. & Avg.~speedup & Delay reduction \\
\hline
\hline
Skype & $2.2\times$ & $7.9\times$\\
Hangout & $4.4\times$ & $7.2\times$\\
Facetime & $1.9\times$ & $8.7\times$\\
\hline
Compound & $1.3\times$ & $4.8\times$\\
TCP Vegas & $1.1\times$ & $2.1\times$\\
LEDBAT & no change & $2.8\times$\\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$\\
%\hline
%Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}

{\footnotesize Adapted from Figure~\ref{f:sproutcompe2e}.}

\end{center}

\subsection{Remy (2013--)}

\textbf{Remy} (Chapter~\ref{chap:remy}) expands Sprout to the
classical problem of \emph{multi-agent} congestion control, where many
independent users may contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of assumptions
about the uncertain network and workload, and an objective to pursue
on behalf of the application. Remy's computer-generated algorithms can
achieve higher performance and greater fairness than some
sophisticated human-designed schemes, including ones that put
intelligence inside the network.
